---
title: "HRT101.S1 - Introduction to Health Research"
author:
- name: Jubayer Hossain
  url: https://jhossain.com
  affiliation: Founder, CHIRAL Bangladesh
  affiliation_url: https://chiralbd.org 
date: "`r Sys.Date()`"
description: |
  This course will give students a foundation in research principles and practice, mainly applied to public health. In addition, we will have weekly lectures covering various topics, including research methodology, data collection methods, statistics, R programming, data visualization(human perception, color theory, principles of visual design), etc.
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r meta, echo=FALSE}
library(metathis)
meta() %>%
  meta_general(
    description = "Make your teaching more robust & reproducible with R Markdown",
    generator = "xaringan and remark.js"
  ) %>% 
  meta_name("github-repo" = "https://github.com/chiraleducation/HRT101.S1") %>% 
  meta_social(
    title = "HRT101.S1 - Introduction to Health Research",
    url = "https://chiraleducation.github.io/HRT101.S1/",
    image = "",
    image_alt = "",
    og_type = "website",
    twitter_card_type = "summary_large_image"
  )
```

## Lesson 1: Introduction to Health Research

```{r share-again, echo=FALSE}
xaringanExtra::use_share_again()
```

```{r embed-xaringan-1, echo=FALSE, fig.cap="[Slides](slides/index.html)"}
xaringanExtra::embed_xaringan(url = "slides/HRT101.S1_Lesson2.html", ratio = "16:9")
```

## Lesson 2: Literature Review 
- Why Literature Review
- Smart Google Searching
- Literature Databases
- Developing a Health Research Topic
- Using Google Scholar
- Using PubMed
- Other Biomedical Databases

```{r embed-xaringan-2, echo=FALSE, fig.cap="[Slides](slides/index.html)"}
xaringanExtra::embed_xaringan(url = "slides/HRT101.S1_Lesson2.html", ratio = "16:9")
```

## Lesson 3: Scientific Paper Reading and Research Data Management
- Research Data Management
- Scientific Paper Reading
- Literature Review Matrix

```{r embed-xaringan-3, echo=FALSE, fig.cap="[Slides](slides/index.html)"}
xaringanExtra::embed_xaringan(url = "slides/HRT101.S1_Lesson3.html", ratio = "16:9")
```



## Acknowledgments {.appendix}

This is website made with the [distill package](https://rstudio.github.io/distill/) and a custom theme by [Jubayer Hossain](https://jhossain.com/).
